### 2012-03-12 papers/eccv2012/main.tex
ECCV additional material submitted

\subsubsection{Condition in the joint feature space, not the input
  feature space.}

A common pre--processing operation for statistical learning is to
transform the observed features $\Features$ to zero mean and unit
variance. However, for structured prediction tasks it is the joint
feature space $\JointFtr$ that should be conditioned:
\begin{equation}
  \label{eq:conditioning}
  \JointFtr' = \frac{\JointFtr - \mu}{\sigma^2} ~.
\end{equation}
Ideally one would sample from the joint feature space to determine the
conditioning transformation, but the distribution of inputs and
outputs is generally unknown in an empirical risk minimization
setting. Instead, we use the training set as a proxy. We compute the
empirical mean and variance of
$\{\JointFtr(\Features_k,\Seam_k)\}_{k=1}^n$ at the outset, then apply
the transformation \eqnref{conditioning} after each feature
computation.

@@

For any $\eta>0$, the minimization problem \eqnref{svm-problem} is
equivalent (under the substitution $\Model'=\eta\Model$,
$\xi'=\eta\xi$) to:
\begin{equation}
  \begin{split}
    \min_{\Model',\xi'} &
      \hspace{2mm} 
    \frac{1}{2} \|\Model'\|^2 +
      \eta C \sum_{k=1}^n \xi_k'\\
    s.t. & \hspace{2mm} \forall k, \Seam \neq \Seam_k:~
      \bigl\langle\Model', \JointFtr(\Features_k,\Seam_k)\bigr\rangle -
      \bigl\langle\Model', \JointFtr(\Features_k,\Seam)\bigr\rangle
      \geq
      \frac{1}{\eta} \Loss(\Seam,\Seam_k) - \xi_k' ~.
  \end{split}
  \label{eq:equiv-problem}
\end{equation}
Although any $\eta>0$ preserves the correctness of the optimization
algorithm, we found that choosing $\eta=\mbox{Var}(\Loss)$ improved
numerical stability, since this means the loss terms will have roughly
unit variance. Unfortunately, we cannot use the training set to
estimate $\mbox{Var}(\Loss)$ since the loss for the ground truth
reconstruction is always zero. Instead we computed
$\Loss(\Features_k,\Seam_j)$ for each $k \neq j$ in the training
set. This is not an ideal estimate, but we found that it worked well
in practice.

>>>>

\subsubsection{Condition in the joint feature space, not the input
  feature space.}
gi
A common pre--processing operation for statistical learning is to
transform the observed features $\Features$ to zero mean and unit
variance. However, for structured prediction tasks it is the joint
feature space $\JointFtr$ that should be conditioned:
\begin{equation}
  \label{eq:conditioning}
  \JointFtr' = \frac{\JointFtr - \mu}{\sigma^2} ~.
\end{equation}
Ideally one would sample from the joint feature space to determine the
conditioning transformation, but the distribution of inputs and
outputs is generally unknown in an empirical risk minimization
setting. Instead, we use the training set as a proxy. We compute the
empirical mean and variance of
$\{\JointFtr(\Features_k,\Seam_k)\}_{k=1}^n$ at the outset, then apply
the transformation \eqnref{conditioning} after each feature
computation.

@@

For any $\eta>0$, the minimization problem \eqnref{svm-problem} is
equivalent (under the substitution $\Model'=\eta\Model$,
$\xi'=\eta\xi$) to:
\begin{equation}
  \begin{split}
    \min_{\Model',\xi'} &
      \hspace{2mm} 
    \frac{1}{2} \|\Model'\|^2 +
      \eta C \sum_{k=1}^n \xi_k'\\
    s.t. & \hspace{2mm} \forall k, \Seam \neq \Seam_k:~
      \bigl\langle\Model', \JointFtr(\Features_k,\Seam_k)\bigr\rangle -
      \bigl\langle\Model', \JointFtr(\Features_k,\Seam)\bigr\rangle
      \geq
      %%% TODO: in the line below 1/eta should be replaced with eta --
      %%% this was incorrect in the review submission!!
      \eta \Loss(\Seam,\Seam_k) - \xi_k' ~.
  \end{split}
  \label{eq:equiv-problem}
\end{equation}
Although any $\eta>0$ preserves the correctness of the optimization
algorithm, we found that choosing $\eta=\mbox{Var}(\Loss)$ improved
numerical stability, since this means the loss terms will have roughly
unit variance. Unfortunately, we cannot use the training set to
estimate $\mbox{Var}(\Loss)$ since the loss for the ground truth
reconstruction is always zero. Instead we computed
$\Loss(\Features_k,\Seam_j)$ for each $k \neq j$ in the training
set. This is not an ideal estimate, but we found that it worked well
in practice.
